A Machine Learning Approach to MLB Catcher Framing

### 2021-12-09 Slides.Rmd
Boosting

- Tested several Random Forest models
  - Nodesize: 10, 30, 50, 70, 90 | # of Trees: 500
  - Compared Out-Of-Bag Error 
```{r, echo=FALSE, fig.width=7, fig.height=3}
load("Data/pitchData.Rda")
load("Model-Outputs/random-forest.Rda")

@@

ggplot(df_gbm_final, aes(x = interaction_depth, y = accuracy, color = as.character(lambda))) +
  geom_line() +
  theme_minimal()+
  geom_point() +
  geom_point(aes(x = 16, y = 0.935), color = "red") +
  labs(x = "Accuracy", y = "Interactin Depth",
       color = "Shrinkage",
       y = "Boosting Accuracy by Interaction Depth and Shrinkage")
```

@@

- Only tuned shrinkage and interaction depth
- Now tune trees with interaction depth of 16 and shrinkage of 0.1

```{r}
load("Model-Outputs/boosting2.Rda")
final_df_gbm %>%
  group_by(trees) %>%
  summarize(accuracy = mean(accuracy)) %>%
  arrange(desc(accuracy)) %>%
  ggplot(aes(x = trees, y = accuracy)) +
  geom_line(color = "goldenrod") +
  theme_minimal() +
  labs(x = "Number of Trees",
       y = "Accuracy",
       title = "Boosting Accuracy by # of Trees")
```

>>>>

- Tested several Random Forest models
  - Nodesize: 10, 30, 50, 70, 90 | # of Trees: 500
  - Compared Out-Of-Bag Error 
```{r, echo=FALSE, fig.width=7, fig.height=4}
load("Data/pitchData.Rda")
load("Model-Outputs/random-forest.Rda")

@@

ggplot(df_gbm_final, aes(x = interaction_depth, y = accuracy, color = as.character(lambda))) +
  geom_line() +
  theme_minimal()+
  geom_point() +
  geom_point(aes(x = 16, y = 0.935), color = "red") +
  labs(x = "Accuracy", y = "Interactin Depth",
       color = "Shrinkage",
       title = "Boosting Accuracy by Interaction Depth and Shrinkage")
```

@@

- Only tuned shrinkage and interaction depth
- Now tune trees with interaction depth of 16 and shrinkage of 0.1
- Trees: 300, 500, 600, 900, 1200

```{r,  fig.width=6, fig.height=3.2}
load("Model-Outputs/boosting2.Rda")
final_df_gbm %>%
  group_by(trees) %>%
  summarize(accuracy = mean(accuracy)) %>%
  arrange(desc(accuracy)) %>%
  ggplot(aes(x = trees, y = accuracy)) +
  geom_line(color = "goldenrod") +
  theme_minimal() +
  labs(x = "Number of Trees",
       y = "Accuracy",
       title = "Boosting Accuracy by # of Trees")
```
